Hydras and Cie (Draft) \\ Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq

### 2021-09-18 doc/JFLA2022/paper.tex
minor corrections

\begin{figure}[h]
  \centering
  \begin{itemize}
\item If $\alpha=0$, then $H'_\alpha (i)= i$ for any natural number $i$.
\item If $\alpha=\beta+1$, then 
$H'_\alpha(i)=H'_\beta(i+1)$ for any $i \in \mathbb{N}$
\item If $\alpha$ is a limit ordinal, then 
$H'_\alpha(i) = H'_{(\canonseq{\alpha}{i+1})}(k)$ for any $i\in \mathbb{N}$.
\end{itemize}
\vspace{4pt}
\inputsnippets{Hprime/HprimeDef}
\caption{The rapidly growing hierarchy $H'$ of arithmetic functions}
\label{fig:Hprime}
\end{figure}

@@

In order to prove formally that the length of the considered
kind of battles is not given by a primitive recursive function, weused the formalisation of primitive recursive functions, part
of Russell O'Connor's contribution on G\"{o}del first incompleteness theorem \cite{OConnor05}. Computability is a key topic in Computer Science teaching. Moreover O'Conors library is a nice illustation on dependently typed functions, so we chose to devote a full chapter to this formalisation, with comments on the definitions and proofs, [counter]-examples and exercises.

\subsection{Documentation with Alectryon}
\begin{todo}
  Interest of Alectryon:
  \begin{itemize}
  \item Despite the frequent changes (improvements) in the Coq scripts, code inclusion (and \textit{Coq}'s anwers are up to date.

  \item Presentation of the main steps of proofs, possibly interleaved with text (Figures \vref{fig:Ex42E0} and \vref{fig:Ex42-schutte},).

>>>>

\begin{figure}[h]
  \centering
  \begin{itemize}
\item If $\alpha=0$, then $H'_\alpha (i)= i$ for any natural number $i$.
\item If $\alpha=\beta+1$, then 
$H'_\alpha(i)=H'_\beta(i+1)$ for any $i \in \mathbb{N}$.
\item If $\alpha$ is a limit ordinal, then 
$H'_\alpha(i) = H'_{(\canonseq{\alpha}{i+1})}(k)$ for any $i\in \mathbb{N}$.
\end{itemize}
\vspace{4pt}
\inputsnippets{Hprime/HprimeDef}
\caption{The rapidly growing hierarchy $H'$ of arithmetic functions}
\label{fig:Hprime}
\end{figure}

@@

In order to prove formally that the length of the considered
kind of battles is not given by a primitive recursive function, weused the formalisation of primitive recursive functions, part
of Russell O'Connor's contribution on G\"{o}del first incompleteness theorem \cite{OConnor05, Goedel}.
For this purpose, and above all by consideration of the scientific interest of this contribution, we chose to host and maintain this work within \textit{Coq-Community}.

Computability is a key topic in Computer Science teaching. Moreover O'Conor's library is a nice illustration of dependently typed programming, so we chose to devote a full chapter to this formalisation, with comments on the definitions and proofs, [counter]-examples and exercises.

\subsection{Documentation with Alectryon}
\begin{todo}
  Interest of Alectryon:
  \begin{itemize}
  \item Despite the frequent changes (improvements) in the Coq scripts, code inclusion and \textit{Coq}'s answers are up to date.

  \item Presentation of the main steps of proofs, possibly interleaved with text (Figures \vref{fig:Ex42E0} and \vref{fig:Ex42-schutte}).
